% main.tex - Minimal IEEE Manuscript Skeleton for SACSE
% Compile with: pdflatex main.tex && bibtex main && pdflatex main.tex && pdflatex main.tex
% Or use latexmk: latexmk -pdf main.tex
% Overleaf: Just hit Recompile (runs BibTeX chain automatically)

\documentclass[conference]{IEEEtran}

%------------------------------------------------------------------------------
% Packages
%------------------------------------------------------------------------------
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{hyperref}

%------------------------------------------------------------------------------
% Document Metadata
%------------------------------------------------------------------------------
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

%------------------------------------------------------------------------------
% Title and Authors
%------------------------------------------------------------------------------
\title{Sovereignty Architecture Cognitive Systems Engineering (SACSE):\\
A Framework for Distributed Cognitive Systems}

\author{
\IEEEauthorblockN{[Author Name]}
\IEEEauthorblockA{\textit{[Department/Affiliation]} \\
[City, Country] \\
[email@example.com]}
}

\maketitle

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
\begin{abstract}
This paper presents the Sovereignty Architecture Cognitive Systems Engineering 
(SACSE) methodology, a comprehensive framework for designing, implementing, 
and deploying distributed cognitive systems. We introduce a catalog of 100 
engineering techniques organized into 10 thematic clusters, addressing 
challenges from cognitive architecture foundations to governance and compliance. 
The framework emphasizes sovereignty, interpretability, and alignment while 
maintaining practical applicability for enterprise-scale deployments. 
[PLACEHOLDER: Expand with specific contributions and results.]
\end{abstract}

%------------------------------------------------------------------------------
% Keywords
%------------------------------------------------------------------------------
\begin{IEEEkeywords}
cognitive architecture, distributed systems, sovereignty, artificial intelligence, 
systems engineering, alignment, interpretability
\end{IEEEkeywords}

%------------------------------------------------------------------------------
% Introduction
%------------------------------------------------------------------------------
\section{Introduction}

The increasing complexity of cognitive systems demands rigorous engineering 
methodologies that balance capability with safety, interpretability, and 
governance requirements. The Sovereignty Architecture Cognitive Systems 
Engineering (SACSE) methodology addresses this need by providing a structured 
approach to distributed cognitive system design.

[PLACEHOLDER: Expand introduction with problem statement, motivation, and paper structure.]

%------------------------------------------------------------------------------
% Background and Related Work
%------------------------------------------------------------------------------
\section{Background and Related Work}

[PLACEHOLDER: Literature review covering:
\begin{itemize}
    \item Cognitive architectures (SOAR, ACT-R, etc.)
    \item Distributed systems consensus mechanisms
    \item AI safety and alignment research
    \item Enterprise AI governance frameworks
\end{itemize}
]

%------------------------------------------------------------------------------
% Methodology
%------------------------------------------------------------------------------
\section{Methodology}
\label{sec:methodology}

The SACSE methodology comprises 100 engineering techniques organized into 
10 thematic clusters. Each cluster addresses a distinct aspect of distributed 
cognitive system engineering, from foundational architecture patterns to 
governance and compliance requirements.

\subsection{Overview of Engineering Technique Clusters}

The complete catalog of techniques is organized as follows:

\begin{enumerate}
    \item \textbf{Cognitive Architecture Foundations} -- Core patterns for 
          hierarchical state management, attention mechanisms, and memory systems.
    \item \textbf{Distributed Consensus Mechanisms} -- Protocols for agreement, 
          consistency, and coordination in multi-agent environments.
    \item \textbf{Knowledge Representation and Reasoning} -- Formalisms for 
          encoding and manipulating structured knowledge.
    \item \textbf{Security and Sovereignty Patterns} -- Cryptographic and 
          access control techniques for sovereign operation.
    \item \textbf{Agent Communication and Coordination} -- Protocols and 
          architectures for multi-agent interaction.
    \item \textbf{Learning and Adaptation Systems} -- Techniques for 
          continuous improvement and domain adaptation.
    \item \textbf{Interpretability and Alignment} -- Methods for ensuring 
          human-understandable and value-aligned behavior.
    \item \textbf{Infrastructure and Deployment} -- Cloud-native patterns 
          for production cognitive workloads.
    \item \textbf{Evaluation and Benchmarking} -- Frameworks for systematic 
          capability assessment.
    \item \textbf{Governance and Compliance} -- Processes for regulatory 
          alignment and ethical oversight.
\end{enumerate}

See Appendix~\ref{sec:appendix-techniques} for the full catalog of 100 
techniques with detailed descriptions and citations.

[PLACEHOLDER: Expand with methodology details, selection criteria, and validation approach.]

%------------------------------------------------------------------------------
% Implementation
%------------------------------------------------------------------------------
\section{Implementation}

[PLACEHOLDER: Implementation details, case studies, and practical considerations.]

%------------------------------------------------------------------------------
% Evaluation
%------------------------------------------------------------------------------
\section{Evaluation}

[PLACEHOLDER: Evaluation methodology, results, and analysis.]

%------------------------------------------------------------------------------
% Discussion
%------------------------------------------------------------------------------
\section{Discussion}

[PLACEHOLDER: Discussion of findings, limitations, and implications.]

%------------------------------------------------------------------------------
% Conclusion
%------------------------------------------------------------------------------
\section{Conclusion}

[PLACEHOLDER: Summary of contributions and future work directions.]

%------------------------------------------------------------------------------
% Acknowledgments (optional)
%------------------------------------------------------------------------------
% \section*{Acknowledgments}
% [PLACEHOLDER: Acknowledgments if needed.]

%------------------------------------------------------------------------------
% Appendix
%------------------------------------------------------------------------------
\appendix
\input{appendixA}

%------------------------------------------------------------------------------
% References
%------------------------------------------------------------------------------
\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
